%------------------------
% Curriculum Vitae - Chanhyuk Lee
%------------------------

% Document class and font size
\documentclass[a4paper,9pt]{extarticle}

% Packages
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{changepage}
\usepackage[sfdefault]{inter}
\setlength{\parindent}{0pt}

% Formatting
\setlist{noitemsep}
\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}[\titlerule]
\titlespacing*{\section}{0pt}{\baselineskip}{0.5\baselineskip}

% Publication label/ref commands
\newcommand{\publabel}[1]{\textbf{#1.}\phantomsection\label{pub:#1}}
\newcommand{\pubref}[1]{\hyperref[pub:#1]{\textbf{[#1]}}}

%-------------------------------------------------------------------------------
\begin{document}

\pagestyle{empty}

% Header
\begin{center}
    \textbf{\Large Chanhyuk Lee}\\[3pt]
    \textbf{Curriculum Vitae}\\[1pt]
    Seoul/Daejeon, South Korea | \href{mailto:chan3684@kaist.ac.kr}{chan3684@kaist.ac.kr} | \href{https://david3684.github.io}{david3684.github.io}
\end{center}

%------------------------
\section*{EDUCATION}
\textbf{M.S. in Computer Science} \hfill Mar. 2025 -- Present \\
Korea Advanced Institute of Science and Technology (KAIST) \\
School of Computing \\
Advisor: Prof. Seunghoon Hong \\

\textbf{B.S. in Computer Science and Chemistry} (Double Major) \hfill Mar. 2019 -- Feb. 2025 \\
Korea Advanced Institute of Science and Technology (KAIST) \\

\textbf{Gyeonggi Science High School for Gifted} \hfill Mar. 2016 -- Feb. 2019 \\

%------------------------
\section*{PUBLICATIONS}

\textbf{Infinite Mask Diffusion for Few-Step Distillation} \\
Jaehoon Yoo, Wonjung Kim, \textbf{Chanhyuk Lee}, Seunghoon Hong. \\
\textit{Under Review}, 2026.

{\setlength{\parskip}{10pt}
\publabel{P2} \href{https://arxiv.org/abs/2602.16813}{\textbf{One-step Language Modeling via Continuous Denoising}} \\
\textbf{Chanhyuk Lee}, Jaehoon Yoo, Manan Agarawal, Sheel Shah, Jerry Huang, \\
Aditi Raghunathan, Seunghoon Hong, Nicholas M. Boffi, Jinwoo Kim. \\
\textit{arXiv Preprint}, 2026.

\publabel{C2} \href{https://arxiv.org/abs/2503.22178}{\textbf{AdaRank: Adaptive Rank Pruning for Enhanced Model Merging}} \\
\textbf{Chanhyuk Lee}, Jiho Choi, Chanryeol Lee, Donggyun Kim, Seunghoon Hong. \\
\textit{International Conference on Learning Representations (\textbf{ICLR})}, 2026.

\publabel{C1} \href{http://arxiv.org/abs/2509.07530}{\textbf{Universal Few-Shot Spatial Control for Diffusion Models}} \\
Kiet T. Nguyen, \textbf{Chanhyuk Lee}, Donggyun Kim, Donghoon Lee, Seunghoon Hong. \\
\textit{Conference on Neural Information Processing Systems (\textbf{NeurIPS})}, 2025.

\publabel{P1} \href{https://arxiv.org/abs/2412.12153}{\textbf{Revisiting Weight Averaging for Model Merging}} \\
Jiho Choi*, Donggyun Kim*, \textbf{Chanhyuk Lee}, Seunghoon Hong. \\
\textit{arXiv Preprint}, 2024.

}

%------------------------
\section*{EXPERIENCE}
\textbf{Graduate Research Assistant} \hfill Mar. 2025 -- Present \\
Vision and Learning Lab, KAIST CS\\
Advisor: Prof. Seunghoon Hong \\
Research on diffusion language models, model merging, parameter alignement.

{\setlength{\parskip}{10pt}

\textbf{Undergraduuate Researcher} \hfill July. 2024 -- Feb. 2025 \\
Vision and Learning Lab, KAIST CS\\
Advisor: Prof. Seunghoon Hong \\
Research on model merging and few-shot learning.

\textbf{Undergraduuate Researcher} \hfill Jan. 2024 -- June. 2024 \\
CVML Lab, KAIST AI\\
Advisor: Prof. Hyunjung Shim \\
Research on efficient neural network via weight quantization.

\textbf{Military Service}, Republic of Korea Army \hfill Jan. 2022 -- July. 2023 

\textbf{Undergraduuate Researcher} \hfill Jan. 2020 -- June. 2021 \\
M-Design Lab, KAIST Chem\\
Advisor: Prof. Hyungjun Kim \\
Research on simulating acid-base proton transfer via DFT.

}

%------------------------
% \section*{ACADEMIC SERVICES}
% \textbf{Conference Reviewer:} % add any you've reviewed for

% \textbf{Journal Reviewer:} % add any you've reviewed for

%------------------------
\section*{TEACHING}
\textbf{Teaching Assistant, KAIST School of Computing}

Introduction to Deep Learning (CS371) \hfill Fall 2025

Elements of AI (CS103) \hfill Spring 2025 \\

\textbf{Teaching Assistant, Samsung Electronics}

Samsung Research AI Expert Program \hfill 2025 \\

\textbf{Student Mentoring}

Yeonwoo Choi, B.S Student @ KAIST \hfill 2026-

Chanryeol Lee, B.S Student @ KAIST \pubref{C2} $\rightarrow$ M.S Student @ KAIST \hfill 2024-2025

%------------------------
\section*{HONORS}
\textbf{Awards}

KAIST School of Computing Best TA Award \hfill 2025

Samsung Humantech Paper Awards (Highschool Track) \hfill 2018

%------------------------
\section*{SKILLS}
\textbf{Programming Languages:} Python, C/C++ \\
\textbf{Languages:} Korean (Native), English (Fluent, IBT TOEFL: 108)

%------------------------
\section*{LINKS}
\textbf{GitHub:} \href{https://github.com/david3684}{github.com/david3684} \\
\textbf{Google Scholar:} \href{https://scholar.google.com/citations?user=mpSpDHcAAAAJ}{scholar.google.com/citations?user=mpSpDHcAAAAJ} \\
\textbf{LinkedIn:} \href{https://www.linkedin.com/in/chanhyuk-lee-18b01528b}{linkedin.com/in/chanhyuk-lee-18b01528b}

%------------------------
\section*{REFERENCES}
\textbf{Seunghoon Hong}, Associate Professor at KAIST \\
\href{mailto:seunghoon.hong@kaist.ac.kr}{seunghoon.hong@kaist.ac.kr}

\end{document}